A new method to estimate dark matter halo concentrations

### 2015-08-21 paper/article.tex
integrated 2 figures

\section{Introduction}
\label{sec:introduction}
In the concordance cosmology paradigm the matter content of the
Universe is dominated by dark matter, a collisionless fluid shaped by
gravitational interactions.
In the last three decades numerical experiments have made possible the
simulation of dark matter dominated universes, yielding valuable
insights on the large scale structure formation process.
This description shows a remarkable success in comparisons against
observations of galaxy distributions on large scales
\citep{Springel2005,2011ApJ...740..102K}.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20$.
    \label{fig:results_mocks_conc_20}}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20000.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20000$.
    \label{fig:results_mocks_conc_20000}}
\end{figure}

>>>>

\section{Introduction}
\label{sec:introduction}
In the concordance cosmology the matter content of the
Universe is dominated by dark matter, a collisionless fluid shaped by
gravitational interactions.
In the last three decades numerical experiments have made possible the
simulation of dark matter dominated universes, yielding valuable
insights on the large scale structure formation process.
This description shows a remarkable success in comparisons against
observations of galaxy distributions on large scales
\citep{Springel2005,2011ApJ...740..102K}.

@@

\begin{figure*}

  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}

\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
    \label{fig:results_mocks_conc_20}}
\end{figure*}
